ANTs brain morphology

### 2017-04-24 evaluation/antsvfreesurfer2.Rmd
ENH:  ASNR 2017

![](./evaluation/figures/pipeline.png)

@@

![](./evaluation/figures/templates.png)

* Templates representing the average mean shape and intensity are built directly from the
* cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
* Acquisition and anonymization (e.g. defacing) protocols are often different.

@@

![](./evaluation/figures/templatePriors.png)

@@

![](./evaluation/figures/brainExtraction.png)

@@

![](./evaluation/figures/brainSegmentation.png)

@@

![](./evaluation/figures/corticalThicknessEstimation.png)

@@

_But without ground truth, how does one evaluate the pipeline?_

@@

@@

@@

![](./evaluation/figures/evaluation.png)

@@

![](./evaluation/figures/agePredictionPerSite.png)

@@

![](./evaluation/figures/antsvfreesurfer_Importance.png)

ANTs (left) vs. FreeSurfer (right)

@@

![](./evaluation/figures/antsvfreesurfer_regionalPlots.png)

>>>>

\begin{centering}

\includegraphics[width=4.5in]{./evaluation/figures/pipeline.png}

\end{centering}

@@

\begin{centering}

\includegraphics[width=3in]{./evaluation/figures/templates.png}

\end{centering}

\small

* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.  
* Acquisition and anonymization (e.g. defacing) protocols are often different.

@@

\begin{centering}

\includegraphics[width=2.5in]{./evaluation/figures/templatePriors.png}

\end{centering}

\small

@@

\begin{centering}

\includegraphics[width=3.5in]{./evaluation/figures/brainExtraction.png}

\end{centering}

\small

@@

\begin{centering}

\includegraphics[width=3.5in]{./evaluation/figures/brainSegmentation.png}

\end{centering}

\small

@@

\begin{centering}

\includegraphics[width=4in]{./evaluation/figures/corticalThicknessEstimation.png}

\end{centering}

\small

@@

\begin{centering}

\Large

{\bf But without ground truth, how does one evaluate the pipeline?}

\end{centering}

@@

\begin{centering}

@@

\end{centering}

@@

\begin{centering}

\includegraphics[width=4in]{./evaluation/figures/evaluation.png}

\end{centering}

@@

\begin{centering}

\includegraphics[width=4in]{./evaluation/figures/agePredictionPerSite.png}

\end{centering}

@@

\begin{centering}

\small
ANTs (left) vs. FreeSurfer (right)

\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_Importance.png}

\end{centering}

@@

\begin{centering}

\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_regionalPlots.png}

\end{centering}
